Clustering Beat-Chroma Patterns\\ in a Large Music Database

### 2010-07-08 Paper/Poster/poster.tex
fixed the algorithm
good orientation

\documentclass[landscape,a0b,final]{a0poster}

@@

%%% Unisiegel
\begin{minipage}[c][9cm][c]{0.1\textwidth}
  \begin{center}
    \includegraphics[width=7cm,angle=0]{labrosa-logo.eps}
  \end{center}
\end{minipage}
%%% Titel
\begin{minipage}[c][9cm][c]{0.78\textwidth}
  \begin{center}
    {\sc \Huge Clustering Beat-Chroma Patterns in a Large Music Database}\\[10mm]
    {\Large Thierry Bertin-Mahieux $^\dagger$, Ron J. Weiss $^\ddagger$ and Daniel P. W. Ellis $^\dagger$\\[3.5mm]
     \large $\dagger$ LabROSA, Dept. of Electrical Engineering, Columbia University \\
     \large $\ddagger$ MARL, New York University \\
    \tt{\{thierry,ronw,dpwe\}@ee.columbia.edu}}
  \end{center}
\end{minipage}
%%% GK-Logo
\begin{minipage}[c][9cm][c]{0.1\textwidth}
  \begin{center}
    \includegraphics[width=7cm,angle=0]{seas-logo.eps}
  \end{center}
\end{minipage}

@@

\myfig[0]{code_axis.ps}{.2}

@@

\begin{minipage}{\columnwidth}
%\caption{Pseudocode of Vector Quantization}
\begin{algorithmic}
\begin{algorithm}[H]
\STATE$\ell$ learning rate
\STATE$\{P_n\}$ set of patches
\STATE$\{C_k\}$ codebook of $K$ codes
\REQUIRE $0 < \ell \leq 1$
\FOR{$nIters$}
\FOR{$p \in \{P_n\}$}
\STATE{$c \leftarrow \min_{c \in C_k} \mbox{dist}(p,c)$}
\STATE{$c \leftarrow c + (p - c) * \ell$}
\ENDFOR
\ENDFOR
\RETURN $\{C_k\}$
\end{algorithm}
\end{algorithmic}
\end{minipage}

%%% Section 4
\vspace{0cm}
\begin{center}
  \pbox{0.8\columnwidth}{}{linewidth=2mm,framearc=0.1,linecolor=lightred,fillstyle=gradient,gradangle=0,gradbegin=white,gradend=whitepink,gradmidpoint=1.0,framesep=1em}{
    \begin{center}
      \large Pattern Analysis
    \end{center}}
\end{center}

@@

\vspace{4.0cm}

\begin{minipage}[c][9cm][c]{\columnwidth}

@@

\begin{wrapfigure}{r}{0.5\textwidth}
  \vspace{-20pt}
  \begin{center}
    \includegraphics[width=0.48\textwidth]{conf_mat_per_artist.ps}
  \end{center}
  \vspace{-20pt}
\end{wrapfigure}

>>>>

%\documentclass[landscape,a0b,final]{a0poster}
\documentclass[portrait,a0b,final]{a0poster}

@@

%%% Unisiegel
\begin{minipage}[c][10cm][c]{0.1\textwidth}
  \begin{center}
    \includegraphics[width=7cm,angle=0]{labrosa-logo.eps}
  \end{center}
\end{minipage}
%%% Title
\begin{minipage}[c][9cm][c]{0.78\textwidth}
  \begin{center}
    {\sc \Huge Clustering Beat-Chroma Patterns}\\[5mm]
  {\sc \Huge in a Large Music Database}\\[10mm]
    {\Large Thierry Bertin-Mahieux $^\dagger$, Ron J. Weiss $^\ddagger$ and Daniel P. W. Ellis $^\dagger$\\[3.5mm]
     \large $\dagger$ LabROSA, Dept. of Electrical Engineering, Columbia University \\
     \large $\ddagger$ MARL, New York University \\
    \tt{\{thierry,ronw,dpwe\}@ee.columbia.edu}}
  \end{center}
\end{minipage}
%%% GK-Logo
\begin{minipage}[c][9cm][c]{0.1\textwidth}
  \begin{center}
    \includegraphics[width=7cm,angle=0]{seas-logo.eps}
  \end{center}
\end{minipage}

@@

\myfig[0]{code_axis.ps}{.4}

@@

\vspace{1cm}

\makebox[\columnwidth]{ % replace framebox by makebox

\begin{minipage}[l]{.4\columnwidth}
%\caption{Pseudocode of Vector Quantization}
\begin{algorithmic}
\begin{algorithm}[H]
\vspace{.7cm}
\STATE$\ell$ learning rate
\STATE$\{P_n\}$ set of patches
\STATE$\{C_k\}$ codebook of $K$ codes
%\REQUIRE $0 < \ell \leq 1$
\FOR{$nIters$}
\FOR{$p \in \{P_n\}$}
\STATE{$c \leftarrow \min_{c \in C_k} \mbox{dist}(p,c)$}
\STATE{$c \leftarrow c + (p - c) * \ell$}
\ENDFOR
\ENDFOR
\RETURN $\{C_k\}$
\vspace{.7cm}
\end{algorithm}
\end{algorithmic}
\end{minipage}

\hspace{1.5cm}
\begin{minipage}[r]{.4\columnwidth}
Intuitively:
\begin{list}{\labelitemi}{\leftmargin=1em \labelsep=1em}
\item For each new patch, find the closest codeword.
\item Bring that codewords closer to the patch by some learning
rate.
\item Iterate.
\end{list}
\end{minipage}

}

%%% Section 4
\vspace{2cm}
\begin{center}
  \pbox{0.8\columnwidth}{}{linewidth=2mm,framearc=0.1,linecolor=lightred,fillstyle=gradient,gradangle=0,gradbegin=white,gradend=whitepink,gradmidpoint=1.0,framesep=1em}{
    \begin{center}
      \large Pattern Analysis
    \end{center}}
\end{center}

@@

\begin{minipage}[c]{\columnwidth}

@@

\begin{wrapfigure}{r}{0.6\textwidth}
  \vspace{-20pt}
  \begin{center}
    \includegraphics[width=0.58\textwidth]{conf_mat_per_artist.ps}
  \end{center}
  \vspace{-20pt}
\end{wrapfigure}
